A Simple Minibatch Acceptance Test for MCMC

### 2016-05-18 nips_2016.tex
Added figure about Gaussians to the paper, also fixed the convolution figure and its caption

% Daniel: I decided to put the figure here, so it's closer to the text that references it.
\begin{figure}[t]
    \centering
    \includegraphics[width=\textwidth]{mh_convolution_diagram}
    \caption{
    Three examples of $X_{\rm norm}$ and $X_{\rm corr}$ distributions that convolve to form the
    standard logistic distribution ($\mu=0$ and $s=1$). The three distributions correspond to three
    different standard deviation (SD) values of the $X_{\rm norm}$ distribution (the colors carry
    over to the $X_{\rm corr}$ plot, whose SD values correspond to the $X_{\rm norm}$ SD values).
    This figure must be viewed in color.
    }
    \label{fig:deconvolution}
    \vspace{-10pt}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will be a sequence of images for the Gaussian mixture.}
\end{figure}

>>>>

% Daniel: I decided to put the figure here, so it's closer to the text that references it.
\begin{figure}[t]
    \centering
    \includegraphics[width=1\textwidth]{mh_convolution_diagram_v2}
    \caption{
    Three examples of $X_{\rm norm}$ and $X_{\rm corr}$ distributions that convolve to form the
    standard logistic distribution ($\mu=0$, $s=1$); we use three standard deviation (SD) values of
    $X_{\rm norm}$. The red $X_{\rm norm}$ and $X_{\rm corr}$ curves convolve to form the logistic,
    etc. The $y$-axis is capped at 0.5 for readability. This figure must be viewed in color.
    }
    \label{fig:deconvolution}
    \vspace{-10pt}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{cloud_v01.png}
    \caption{
    {\color{blue}
    Daniel: I'll fix the caption later. Basically, true log posterior, standard/adaptive procedures,
    and our method, using MB=200 out of the 10k samples here. All three used the same proposal
    distribution, a RW with a Gaussian of 0.03.
    }
    }
\end{figure}
